% Resume.tex
\documentclass[12pt,a4paper]{article}
\usepackage{fontawesome}

\usepackage[a4paper,nohead,nofoot,hmargin=1.5cm,vmargin=2cm]{geometry}
\pagestyle{empty}

\usepackage{mdwlist}
\usepackage{enumitem}
\usepackage[final]{hyperref}

\hypersetup{
    hidelinks,
    pdfauthor=Kevin DeLoach,
    pdftitle=Kevin DeLoach
}

\newcommand{\sectionhead}{\normalfont\normalsize\scshape}
\newcommand{\workhead}[3]{\textbf{#1}, \emph{#2} \hfill #3}
\newcommand{\li}{\item[--]}

\begin{document}

\begin{center}
\noindent
{\huge\textsc{Kevin DeLoach}}

\vspace{2mm}

\noindent
% Philadelphia, PA $\cdot$
% (215) 490-8269 $\cdot$
\faEnvelope{ }\href{mailto:kevin@deloach.software}{\bfseries  kevin@deloach.software} $\cdot$
\faLinkedin{ }\href{https://linkedin.com/in/kdeloach}{linkedin.com/in/kdeloach} $\cdot$
\faGithub{ }\href{https://github.com/kdeloach}{github.com/kdeloach}
\end{center}

\noindent\hrulefill

% \section*{\sectionhead Work Experience}
\begin{description}[leftmargin=0em]
    \itemsep0pt
    \parskip3pt

    \item
        \workhead{DeLoach Software}{Founder}{2021-05 -- Present}
        \begin{itemize*}
            \li Create custom software solutions and web applications using Python, Django, Go, and AWS.
        \end{itemize*}

    \item
        \workhead{Streaming Rat}{Co-Founder}{2022-01 -- 2022-09}
        \begin{itemize*}
            \li Developed Ethereum Web3 applications, NFT tools, and Widevine DRM encrypted video streaming using Go, React, GraphQL, Metamask, AWS, and Terraform.
        \end{itemize*}

    \item
        \workhead{Penn Interactive Ventures}{Senior Software Engineer}{2020-01 -- 2021-02}
        \begin{itemize*}
            \li Developed backend APIs for \emph{Barstool Sportsbook}, an online sports betting app, using Python, Django, Go, Postgres, and AWS.
            \li Integrated with \emph{White Hat Gaming}, \emph{Kambi}, \emph{GeoComply}, \emph{Shufti Pro}, and \emph{LexisNexis ThreatMetrix} to support travelling wallet, KYC, and geoverification.
            % \li Designed user flows for registration, KYC, and travelling between states, to comply with regulations from gaming control boards such as \emph{GLI}, \emph{PGCB}, and \emph{DGE}.
        \end{itemize*}

    \item
        \workhead{Warner Bros. Digital Labs}{Senior Software Engineer}{2018-02 -- 2020-01}
        \begin{itemize*}
            \li Developed backend APIs for \emph{DC Universe} and \emph{Boomerang} video streaming platforms using Python, Django, Go, MySQL, and AWS.
            % integrated with \emph{Braintree}, \emph{Swiftype}, and \emph{Discourse}
            \li Collaborated with multiple teams to build APIs for content rights management, predictive assets, search, premium offerings, and compliance with \emph{GDPR} and \emph{CCPA} regulations.
        \end{itemize*}

    \item
        \workhead{TellusLabs}{Software Engineer}{2017-06 -- 2018-02}
        \begin{itemize*}
            \li Created pipelines to collect, process, and ingest terabytes of remote sensing data and satellite imagery, to produce daily crop yield forecasts for \emph{Kernel}, an Earth observations database, using Python, Docker, Airflow, GDAL, NumPy, \mbox{Celery}, RabbitMQ, and AWS.
        \end{itemize*}

    \item
        \workhead{Azavea}{GIS Software Developer}{2014-01 -- 2017-06}
        \begin{itemize*}
            \li Created web-based mapping applications using Python, Django, Docker, PostgreSQL, \mbox{React}, Redux, Leaflet, AWS, Ansible, Terraform, and CloudFormation.
            \li Developed applications for \emph{Stroud Water Research Center}, \emph{The Nature Conservancy}, \emph{The U.S. Army Corps of Engineers}, \emph{The Philadelphia Water Department}, \emph{Department of Records}, and \emph{The New York City Department of Parks \& Recreation}.
            % \li Contributed to \emph{NYC Trees Count!}, \emph{Model My Watershed}, \emph{Coastal Resilience Mapping Portal}, \emph{Unified Land Records System}, and \emph{Raster Foundry} projects
        \end{itemize*}

    \item
        \workhead{IBM Tealeaf Technology}{Software Engineer}{2012-06 -- 2013-09}
        \begin{itemize*}
            \li Integrated \emph{cxOverstat} prototype into \emph{cxImpact} \emph{Browser Based Replay} and implemented UI for \emph{cxOverstat} clickmaps, conversion funnels, and attention maps.
        \end{itemize*}

    \item
        \workhead{ScreenMatter}{Software Developer}{2008-08 -- 2011-12}
        \begin{itemize*}
            \li Developed franchise-oriented CMS, bug tracking software, automation tools, web services, and custom applications for franchise, health care, real estate, and private equity industries.
            \li Generated thousands of search engine optimized local franchisee websites for national franchises such as \emph{Maaco}, \emph{\mbox{CertaPro} Painters}, \emph{Floor Coverings International}, and \emph{Weed Man Lawn Care}.
            \li Built custom applications using C\#/VB .NET, SQL Server, PHP, Flash, Flex, and Adobe AIR.
        \end{itemize*}

    \item
        \workhead{Verve Internet Solutions}{Technical Assistant \& Web Developer}{2007-12 -- 2008-08}
        \begin{itemize*}
            \li Developed proprietary content management system, provided technical support, and produced websites for non-profits using Linux, Apache, MySQL, and PHP.
        %    \li Produced websites for local non-profit organizations: \emph{The Delaware Valley Green Building Council}, \emph{The Consumer Credit Counseling Service of Delaware Valley}, \emph{The Philadelphia Mummers Fancy Brigade Association}, and \emph{Merion Mercy Academy}
        \end{itemize*}

%    \item
%        \workhead{Austin District Music Teachers Association}{Freelance Web Developer}{5/2008 -- 9/2008}
%        \begin{itemize*}
%            \li Developed online portal to schedule events, manage student enrollment, and generate PDFs for approximately 125 teachers.
%        \end{itemize*}

%    \item
%        \workhead{Eshilon Design Inc.}{Freelance Web Production Assistant}{1/2008 -- 3/2008}
%        \begin{itemize*}
%            \li Created cross-browser compatible XHTML/CSS templates from Photoshop PSDs that comply with accessibility and Section 508 standards.
%        \end{itemize*}

%    \item
%        \workhead{Central High School}{Technical Assistant \& Web Developer}{2005-09 -- 2006-07}
%        \begin{itemize*}
%            \li Volunteered with IT department to manage computer labs, diagnose networking issues, and provide technical support for approximately 150 faculty members and 2,300 students.
%            \li Designed website to improve availability of information, increase student engagement, and created a custom CMS featuring role-based permissions, workflow, and extensive logging.
%        \end{itemize*}
\end{description}

% \section*{\sectionhead Technical Skills}
% \begin{description}
%     \itemsep0pt
%     \parskip5pt
%     \item Languages: Python, C\#, VB .NET, Node.js, Java, JavaScript, PHP, PostgreSQL, PostGIS, MS SQL Server, MySQL, SQLite, Flex, ActionScript AS3, XML \Smiley, XSLT, \LaTeX
    % \item Software: Linux, Windows, Apache, NGINX, IIS, Microsoft Visual Studio, SQL Server Management Studio, Vim, Cygwin, Photoshop, Perforce, Git, Subversion, Docker, Vagrant, Ansible, AWS
% \end{description}

\end{document}
